\cventry
    {Software Engineer (Backend)}
    {Zalando SE}
    {Berlin, Germany}
    {September 2022 ‑ present}
    {
      \begin{cvitems}
        \item {Worked on a async microservice styled pipeline that efficiently scrapes competitors' websites to gather valuable information about their product assortments. Currently the system runs with over 150 domains. The system is optimized to run on domain specific schedule and scale as necessary.}
        \item {Maintained consumer specific data pipeline that utilizes the scraped data and own assortment to build business intelligence. These pipelines also ensure validation of scraped items and core business KPI fulfillment. The pipelines are built on AWS step functions and Databricks}
        \item {Took the initiative to design and create multiple dashboards to monitor the health of all asynchronous components with ~150 domain specific services of the system. This increased the visibility of the system for day to day operation.}
        \item {Designed and implemented a automated CI/CD pipeline to deploy monitoring and alerting across different monitoring tools like lightstep, zmon, etc for the microservices with almost no human interaction required reducing 100\% of humane err and required sprint point.}
        \item {Led RCA for production anomolies and implemented preventive measures for the future.}
        \item {Reduced overall system cost by optimizing storage solution for scraped raw pages while retaining the ability to debug erroneous responses in real-time operation issues.}
      \end{cvitems}
    }
    {Python, AWS, Kubernetes, Lightstep, Pyspark, Databricks}
    